Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-07 thesis/paper.tex
reliability

\smallskip \noindent
\textbf{Reliability  }

3
The results should be generalisable to a large extent to any API designers
Should be especially useful for platform/embedded APIs

4
This threat has been counteracted by following a well-reputed guide to case studies \cite{runeson}, and by using analysis methods \cite{grounded} which are conventional. 
The analysis of the data is based around existing theories which should also help reproducibility.
The interview was semi-structured and largely based around the categories of software maintenance and Lehman's laws, which should help reproducibility.

%Internal Validity
\textit{Internal validity} threats for our study have been greatly reduced by the methodologies we have employed. By performing an individual inspection of the API source code, documentation and individual results analysis, internal validity is significantly reduced. Triangulation of the results with the use of interviewing the designers is a key step in reducing potential validity threats in our study.

%External Validity
Regarding \textit{external validity}, generalisability and the appropriateness of our results are at risk. In our study we have striven to ensure that our findings will be as useful as possible to others. Given that there are some similar studies to ours and that ours is an exploratory study, our results will be useful to others who perform similar studies in the future. Our results come from both APIs either in production or soon to be in production. As such, the results of this study will hopefully be of use to the company at which they were studied, be it now for their current API or in the future when they inevitably develop others. Likewise, other companies in similar positions could use the results of our study when creating their own APIs.

%Reliability
The largest \textit{reliability} threat facing our study was the reproducibility. To counter this threat, we have followed a well-proven method for analysing the collected data. Furthermore, as mentioned previously, we have attempted to limit bias and ambiguity in our interview questions where possible. To ensure clarity of the questions, we have field tested the interview with some of our peers, improving the questions based on their feedback.

%Another threat was we were reliant upon being given documentation and code. I.e. they might not give us everything, leave stuff out, ignore things etc.

>>>>

\smallskip \noindent
\textbf{Reliability  } Potential threats to the reliability of our study have to a great extent been reduced by conducting the study according to a well-reputed guide to case studies \cite{runeson2009guidelines}. In addition to that, fragments ( "werd") from additional well-established papers \cite{andersson2007spiral} \cite{seaman1999qualitative} have been used to increase the trustworthiness of the data gathering and data analysis. The analysis was based around well-defined theories that are cemented in academia, to further increase the reproducibility of the study. The semi-structured nature of the interiew, might threaten the reproducibility; but large parts of it were also structured around existing theories.
